Xolotl: An Intuitive and Approachable Neuron and Network Simulator for Research and Teaching

### 2018-08-17 paper/paper.tex
minor fixes to text

In its current form, xolotl is an efficient and easy to use neuron and network simulator that is actively being used in research. 
Results from an early version of this simulator guided intuition in the modeling of a recently characterized Calcium-dependent Potassium channel found in {\em Drosophila} neuromuscular presynaptic terminals (\cite{bronk2018regulation}). Work on the simulator continues in the open at a publicly accessible repository (https://github.com/sg-s/xolotl/), and the library of conductances, synapses and mechanisms that xolotl ships with grows continuously.

@@

The authors acknowledge funding from the National Institute on Drug Abuse (NIDA) through the undergraduate training grant in computational neuroscience R90DA033463 (AH), T32NS007292-31 (SG-S) and R35 NS097343 (EM).

>>>>

In its current form, xolotl is an efficient and easy to use neuron and network simulator that is actively being used in research. 
Results from an early version of this simulator guided intuition in the modeling of a recently characterized Calcium-dependent Potassium channel found in {\em Drosophila} neuromuscular presynaptic terminals (\cite{bronk2018regulation}). Work on the simulator continues in the open at a publicly accessible repository (https://github.com/sg-s/xolotl/), and the library of conductances, synapses and mechanisms that xolotl ships with grows continuously. While this simulator was intended as a research tool, the many worked examples that are built into it demonstrate how it could also be used as a teaching tool.

@@

The authors acknowledge funding from the National Institutes through R90DA033463 (AH), T32NS007292-31 (SG-S) and R35 NS097343 (EM).
